Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-01-10 Master Thesis/synopsis.tex
Update

Now $(T-e)\in\mathbf{A}^1_E$ corresponds to a closed point $P\in \mathbf{P}^1_E$, which in turn corresponds to a valuation in $E(T)$. So the points in the fiber $f'^{-1}(P)$ corresponds to valuations in $F$ above $T-e$. But $T-e$ is inert in $F/E(T)$ since $a\in E[T,a]/(T-e)$ has minimal polynomial $f(e,A)$ over $E[T]/(T-e)$ and $\deg f(e,A) = [F:E(T)]$.

@@

\begin{proof}
With base changing to a Galois extension of $F$, we can assume that $C$ has $F$-rational points. We have the following exact sequence:
\[ 0\longrightarrow \operatorname{Pic}^0(C) \longrightarrow\operatorname{Pic}(C) \longrightarrow \mathbb{Z} \longrightarrow 0  \]
Now $\operatorname{Pic}^0(C)$ can be identified with the $F$-rational points of the Jacobian variety $J$ of $C$. Now $J(F)$ is finitely generated by the Mordell-Weil Theorem \ref{mordell-weil-theorem}, hence $\operatorname{Pic}(C)$ is finitely generated as well.
\end{proof}

@@

\begin{proof}
Let $U = X\setminus S$ and $P_1\in U$ be a closed point. We set:
\[ C_1 = \ker(r_{P_1}|_{K^S}: K^S \to k(P_1)^\times) \]
Since $r_{P_1}|_{k^\times}:k^\times \to k(P_1)^\times$ is injective, we have $C_1\cap k^\times = 1$ and the following map is injective:
\[ C_1 \to\prod_{P\in S}\mathbb{Z},\ x \mapsto (v_P(x))_{P\in S} \]
Therefore, $C_1$ is a free abelian group of finite rank. If $C_1 = 1$, then we set $T = \{P_1\}$ and we are done. Otherwise, let $x\in C_1,\ x\neq 1$. Then there exists an $a\in k^\times$ with the following properties:
\begin{enumerate}[(i)]
\item There exists a point $P_2\in X_0\setminus(S\cup\{P_1\})$ which lies above the prime of $k(x)$ corresponding to the polynomial $x-a\in k[x]$.
\item $a$ is not a root of unity.
\end{enumerate}
We set $C_2 = \ker(r_{P_2}|_{C_1})\subset C_1$. $C_2$ is free abelian of finite rank as well. By requirement $r_{P_2}(x)=a$ and $a\in k^\times$ is not of finite order. It follows $\operatorname{rank}(C_2) < \operatorname{rank}(C_1)$. By repeating this process until $C_r=1$, we get points $P_2,\ldots,P_r\in U_0$, such that the following map is injective:
\[ C_1\to\prod_{i=2}^{r} k(P_i),\ x\mapsto(r_{P_i}(x))_i \]
Finally for $T=\{P_1,\ldots,P_r\}$, the map $r_{S,T}$ is injective. For the second assertion, note that:
\[ \operatorname{coker}(r_{S,T}) \cong\operatorname{coker}\Big(K^S/k^\times \to \prod_{P\in T}k(P)^\times /k^\times \Big) \]
Since $K^S/k^\times$ is finitely generated, Lemma \ref{5.2} (iii) and Lemma \ref{5.3} (ii) show that the latter group is free-by-finite.
\end{proof}

>>>>

Now $T-e\in E[T]$ corresponds to a closed point $P\in \mathbf{P}^1_E$, which in turn corresponds to a valuation in $E(T)$. So the points in the fiber $f'^{-1}(P)$ corresponds to valuations in $F$ above $T-e$. But $T-e$ is inert in $F/E(T)$ since $a\in E[T,a]/(T-e)$ has minimal polynomial $f(e,A)$ over $E[T]/(T-e)$ and $\deg f(e,A) = [F:E(T)]$.

@@

\begin{proof}
We have the following exact sequence:
\[ 0\longrightarrow \operatorname{Pic}^0(C) \longrightarrow\operatorname{Pic}(C) \longrightarrow \mathbb{Z} \longrightarrow 0  \]
Now $\operatorname{Pic}^0(C)$ can be identified with the $F$-rational points of the Jacobian variety $J$ of $C$. $J(F)$ is finitely generated by the Mordell-Weil Theorem \ref{mordell-weil-theorem}, hence $\operatorname{Pic}(C)$ is finitely generated as well.
\end{proof}

@@

\begin{proof}
Let $U = X\setminus S$ and $P_1\in U$ be a closed point. We set:
\[ C_1 = \ker(r_{P_1}|_{K^S}: K^S \to k(P_1)^\times) \]
Since $r_{P_1}|_{k^\times}:k^\times \to k(P_1)^\times$ is injective, we have $C_1\cap k^\times = 1$ and the following map is injective:
\[ C_1 \to\prod_{P\in S}\mathbb{Z},\ x \mapsto (v_P(x))_{P\in S} \]
Therefore, $C_1$ is a free abelian group of finite rank. If $C_1 = 1$, then we set $T = \{P_1\}$ and we are done. Otherwise, let $x\in C_1,\ x\neq 1$. Then there exists an $a\in k^\times$ with the following properties:
\begin{enumerate}[(i)]
\item There exists a point $P_2\in X_0\setminus(S\cup\{P_1\})$ which lies above the prime of $k(x)$ corresponding to the polynomial $x-a\in k[x]$.
\item $a$ is not a root of unity.
\end{enumerate}
We set $C_2 = \ker(r_{P_2}|_{C_1})\subset C_1$. $C_2$ is free abelian of finite rank as well. By requirement $r_{P_2}(x)=a$ and $a\in k^\times$ is not of finite order, thus $x\not\in C_2$. It follows $\operatorname{rank}(C_2) < \operatorname{rank}(C_1)$. By repeating this process until $C_r=1$, we get points $P_2,\ldots,P_r\in U_0\setminus S$, such that the following map is injective:
\[ C_1\to\prod_{i=2}^{r} k(P_i),\ x\mapsto(r_{P_i}(x))_i \]
Finally for $T=\{P_1,\ldots,P_r\}$, the map $r_{S,T}$ is injective. For the second assertion, note that:
\[ \operatorname{coker}(r_{S,T}) \cong\operatorname{coker}\Big(K^S/k^\times \to \prod_{P\in T}k(P)^\times /k^\times \Big) \]
Since $K^S/k^\times$ is finitely generated, Lemma \ref{5.2} (iii) and Lemma \ref{5.3} (ii) show that the latter group is free-by-finite.
\end{proof}
